GPU-friendly Stroke Expansion

### 2024-04-29 paper.tex
fix phrasing

Our GPU implementation targets graphics APIs that do not support dynamic memory allocation in shader code (unlike CUDA which provides the equivalent of \emph{malloc}). This makes it necessary to allocate the storage buffer in advance with enough memory to store the output, however, the precise memory requirement is unknown prior to running the shader.

>>>>

Our GPU implementation targets graphics APIs that do not support dynamic memory allocation in shader code (in contrast to CUDA, which provides the equivalent of \emph{malloc}). This makes it necessary to allocate the storage buffer in advance with enough memory to store the output, however, the precise memory requirement is unknown prior to running the shader.
